---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# wikiplantbaser

<!-- badges: start -->
<!-- badges: end -->

Wikiplantbaser provides an easy access to the floristic records stored in 
the Wikiplantbase #Italia online database (http://bot.biologia.unipi.it/wpb/italia).
As of November 2022, the database stores around 700k georeferenced occurrence points 
for approximately 4k plant names. Wikiplantbaser is not meant as a tool for a massive
download of hundreds of thousands of records. Instead, it is geared to facilitate the 
download of subsets of data, especially at genus or section level, and the production
of publication-grade maps.

Its main workhorse is wpb_getByTaxon(), that accepts a vector of plant names as parameter
and returns all occurrence points for those names. Partial names are accepted: for instance,
the name "Crocus" will return all occurrences of all species of Crocus stored in the database.

## Installation

You can install the development version of wikiplantbaser from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("gibedini/wikiplantbaser")
```

## Example

This is a basic example which shows you how to obtain all occurrence points 
for Crocus etruscus Parl.:

```{r example}
library(wikiplantbaser)
wpb_getByTaxon(c("Crocus etruscus Parl."))
## basic example code
```

The above line will return a dataframe with eight columns and a number of rows matching 
the number of records extracted from the database. A call with a partial name, like this:


```{r example2}
library(wikiplantbaser)
wpb_getByTaxon(c("Crocus"))
```

will return all occurrences of all species of Crocus.
